---
title: 'P8105 HW1'
author: 'Jingfeng Cao'
output: github_document
---

## Problem 1

### load library
```{r}
library(moderndive)
library(tidyverse)
```

### load data

```{r}
data("early_january_weather")
```

### short discription

This dataset contains variables of `r names(early_january_weather)`. And it contains `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. The mean temperature is `r mean(early_january_weather$temp)`. 

### scatterplot of temp vs time_hour

Draw a scatterplot of temp (y) vs time_hour (x) and save as `scatterplot_temp_vs_time_hour.png`.
```{r}
ggplot(early_january_weather,aes(x = time_hour, y = temp, color = humid)) + geom_point()
ggsave('scatterplot_temp_vs_time_hour.png')
```

The patterns of this plot:
The temp has periodically waves, which might be because of high temperature during daytimes and low during nights. During the time in this dataset, the temperature dropped to the lowest and gradually increase in trend. After reaching the highest on about Jan 14, the temperature suddenly dropped and reached the similar level of the beginning. The humid is high at a short time interval on and before Jan 14, and is slightly high at some time point around Jan 07. 

## Problem 2







